Approximation as Differentiation: Notes

### 2025-05-16 main/formal-structures.tex
Prefer direct composition notation for reindexing functor.
Nope, need to keep reindexing notation distinct from composition otherwise things get confusing.

Any function $f: X \to Y$ induces a \emph{reindexing} functor $- \comp f: \Func{Y}{\cat{C}} \to
\Func{X}{\cat{C}}$ which sends any $Y$-indexed family $F$ over $\cat{C}$ to the $X$-indexed family $F \comp f$
(regarding $f$ as a functor between $X$ and $Y$ as discrete categories) and any family of morphisms $\eta: F
\to G$ to $\eta \comp f: F \comp f \to G \comp f$ with $(\eta \comp f)_x = \eta_{f(x)}$.

>>>>

\begin{definition}[Reindexing]
For any function $f: X \to Y$ define the \emph{reindexing} functor $\reindex{-}{f}: \Func{Y}{\cat{C}} \to
\Func{X}{\cat{C}}$ which sends any $Y$-indexed family $F$ over $\cat{C}$ to the $X$-indexed family
$\reindex{F}{f} = F \comp f$ (regarding $f$ as a functor between $X$ and $Y$ as discrete categories) and any
family of morphisms $\eta: F \to G$ to $\reindex{\eta}{f}: \reindex{F}{f} \to \reindex{G}{f}$ with
$\reindex{\eta}{f}(x) = \eta(f(x))$.
\end{definition}

Although reindexing just precomposes with $f$, writing it as $\reindex{-}{f}$ avoids notational confusion when
combining composition of morphisms in $\Func{X}{C}$ with reindexing.
